Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: fig refing

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
\caption{(Color online).~Similar to Fig.~\ref{fig:dCS_exec_sum}, but for dCS gravity.
%
% ~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
% GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
% %
% In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
% in spin QNM correction.
%
We stress that posteriors obtained including $n=1$ corrections, violated conditions~\eqref{eq:parspec_bound}
and therefore should not be used to draw meaningful conclusions. We show them for illustrative purposes
and also to emphasize the importance of taking conditions~\eqref{eq:eft_bound} and~\eqref{eq:parspec_bound}
simultaneously into consideration when analyzing the results of the parameter estimation.
}
\label{fig:dCS_exec_sum}
\end{figure}

@@

Let us now consider the quartic EFT of GR as our final example.
%
In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR
%
We find that both the ``EFT''~\eqref{eq:eft_bound} and ``ParSpec''~\eqref{eq:parspec_bound} are satisfied,
hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
%
As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_f$ before $\varepsilon = 1/2$.
%
Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
%
\begin{equation}
    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km}\,.
\end{equation}

>>>>

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for dCS gravity.
%
% ~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
% GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
% %
% In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
% in spin QNM correction.
%
We stress that posteriors obtained including $n=1$ corrections, violate conditions~\eqref{eq:parspec_bound}
and therefore should not be used to draw meaningful conclusions. We show them for illustrative purposes
and also to emphasize the importance of taking conditions~\eqref{eq:eft_bound} and~\eqref{eq:parspec_bound}
simultaneously into consideration when analyzing the results of the parameter estimation.
}
\label{fig:dCS_exec_sum}
\end{figure}

@@

Let us now consider the quartic EFT of GR as our final example.
%
In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR.
%
We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
%
As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_f$ before $\varepsilon = 1/2$.
%
Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
%
\begin{equation}
    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km}\,.
\end{equation}
